Automated reading of residual plots with computer vision models

### 2024-01-29 paper/paper.Rmd
add delta and gamma metrics

experiment <- vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  select(unique_lineup_id, attention_check, null_lineup,
         answer, effect_size, conventional_p_value,
         p_value, type, shape, a, b, x_dist, e_dist,
         e_sigma, include_z, k, n)

@@

>>>>

experiment <- vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  select(unique_lineup_id, attention_check, null_lineup, prop_detect,
         answer, effect_size, conventional_p_value,
         p_value, type, shape, a, b, x_dist, e_dist,
         e_sigma, include_z, k, n)

@@

```{r fig.cap = "A weighted detection rate vs $\\delta$-differnence plot."}
lineup_vss <- readRDS(here::here("paper/data/lineup_vss.rds"))
lineup_vss <- lineup_vss %>%
  group_by(unique_lineup_id) %>%
  mutate(delta_diff = vss[!null] - max(vss[null])) %>%
  mutate(gamma_diff = sum(vss[null] > vss[!null]))

experiment %>%
  left_join(lineup_vss %>%
              group_by(unique_lineup_id) %>%
              summarise(delta_diff = first(delta_diff), gamma_diff = first(gamma_diff))) %>%
  ggplot() +
  geom_point(aes(delta_diff, prop_detect)) +
  geom_smooth(aes(delta_diff, prop_detect), se = FALSE) +
  ylab("Weighted detection rate") +
  xlab(expression(gamma-difference)) +
  theme_light()
```

```{r fig.cap = "A weighted detection rate vs $\\gamma$-number of extreme nulls plot."}
experiment %>%
  left_join(lineup_vss %>%
              group_by(unique_lineup_id) %>%
              summarise(delta_diff = first(delta_diff), gamma_diff = first(gamma_diff))) %>%
  ggplot() +
  geom_point(aes(gamma_diff, prop_detect)) +
  ylab("Weighted detection rate") +
  xlab(expression(gamma-number~of~extreme~nulls)) +
  theme_light()
```

```{r fig.cap = "A weighted detection rate vs $\\delta$-differnence plot for lineups evaluated by 11 people."}
experiment %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  left_join(lineup_vss %>%
              group_by(unique_lineup_id) %>%
              summarise(delta_diff = first(delta_diff), gamma_diff = first(gamma_diff))) %>%
  ggplot() +
  geom_point(aes(delta_diff, prop_detect)) +
  geom_smooth(aes(delta_diff, prop_detect), se = FALSE) +
  ylab("Weighted detection rate") +
  xlab(expression(delta-difference)) +
  theme_light()
```

```{r fig.cap = "A weighted detection rate vs $\\gamma$-number of extreme nulls plot for lineups evaluated by 11 people."}
experiment %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  left_join(lineup_vss %>%
              group_by(unique_lineup_id) %>%
              summarise(delta_diff = first(delta_diff), gamma_diff = first(gamma_diff))) %>%
  ggplot() +
  geom_point(aes(gamma_diff, prop_detect)) +
  ylab("Weighted detection rate") +
  xlab(expression(gamma-number~of~extreme~nulls)) +
  theme_light()
```

### 2024-01-29 paper/paper.tex
add delta and gamma metrics

>>>>

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-3-1}

\caption{A weighted detection rate vs $\delta$-differnence plot.}\label{fig:unnamed-chunk-3}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-4-1}

\caption{A weighted detection rate vs $\gamma$-number of extreme nulls plot.}\label{fig:unnamed-chunk-4}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-5-1}

\caption{A weighted detection rate vs $\delta$-differnence plot for lineups evaluated by 11 people.}\label{fig:unnamed-chunk-5}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{paper_files/figure-latex/unnamed-chunk-6-1}

\caption{A weighted detection rate vs $\gamma$-number of extreme nulls plot for lineups evaluated by 11 people.}\label{fig:unnamed-chunk-6}
\end{figure}
